### 2025-04-19 futureWork/rlHedging.tex
asd

Consider a \gls{va} contract whose delta hedge portfolio at any time~$t$, $t=0,1,\ldots,T-1$, consists of $\Delta_t$ units in the underlying stock and $B_t$ amount of a risk-free zero-coupon bond maturing at time $T$.
The value of the hedge portfolio at time~$(t-1)$ is:
\begin{equation*}
    H_{t-1} = \Delta_{t-1} S_{t-1} + B_{t-1},
\end{equation*}
where $S_t$ is the underlying stock price and any time $t>0$.
This hedge portfolio is brought forward to the next rebalancing time~$t$, when its value becomes:
\begin{equation*}
    H_{t}^{bf} = \Delta_{t-1} S_{t} + B_{t-1}e^{r}.
\end{equation*}
Therefore, the time~$t$ hedging error, i.e., the cash flow incurred by the insurer due to rebalancing at time~$t$, is
\begin{equation}
    HE_t = H_t - H^{bf}_t, \quad t=1,\ldots, T-1.
\end{equation}
The P\&L of the \gls{va} contract includes the cost of the initial hedge ($H_0$), the hedging errors~\eqref{eq2:hedgingerror}, the unwinding of the hedge at maturity ($H^{bf}_T$), and the contract payout at time~$t\in \{0,\ldots,T\}$.
Mathematically, the present value of the liability for a \gls{gmmb} contract is 
\begin{align} \label{eq3:lossGMMB}
L   & = H_0 - e^{-rT} H^{bf}_T + \sum_{t=1}^{T-1} e^{-rt} HE_t + \sum_{t=1}^T e^{-rt} C_t - \sum_{t=1}^T e^{-rt} F_t\eta_n + e^{-rT} (G_t - F_t)^+  \nonumber \\ 
    & = e^{-rT} (G_T - F_{T^+})^+ + \sum_{t=1}^T e^{-rt}  \left( \Delta_{t-1} (S_{t-1} - e^{-r} S_t) + C_t - F_t\eta_n \right) 
\end{align}
where the equality holds by a rearrangement of terms and a telescopic sum simplification of $e^{-rt}B_t$, $t=0,\ldots,T-1$, and $C_t := C \cdot S_{t-1} \cdot |\Delta_t - \Delta_{t-1}|$ is the tranaction cost at time $t$~\citep{garleanu2013dynamic}.
Hence, the present liability consist of the hedging errors, the transaction costs, the net management fees, and the contract payouts.
Similarly, the present value of the liability for a \gls{gmwb} contract is
\begin{equation} \label{eq3:lossGMWB}
L = \sum_{t=1}^T e^{-rt}  \left( \Delta_{t-1} (S_{t-1} - e^{-r} S_t) + C_t - F_t\eta_n \right)
\end{equation}
The \gls{gmwb} payout is implicitly included in $F_t\eta_n$.
Both Equation~\eqref{eq3:lossGMMB} and Equation~\eqref{eq3:lossGMWB} neglect the transaction cost to liquidate the hedge portfolio at maturity.
The discrete-time hedging problem of VAs can be conveniently formulated as an \gls{mdp}, where the states, actions, transition probabilities, policies, and rewards are defined as follows.

\subsection{State Space}

The state space $\mathcal{S}$ represents all the information needed to characterize the hedging environment.
In a \gls{va} hedging problem, $\mathbf{s}_t$, the information available to a hedging agent at each time $t$ is 
$$\mathbf{s}_t := (S_t, F_t, G_t, \tau, \Delta_{t-1}) \in \mathcal{S}.$$
where $\tau$ is the remaining time to maturity and $\Delta_{t-1}$ is the previous hedging weight.
The hedging environment is partially observed, e.g., the agent does not have access to the contract specifications.
It has to learn a representation of the relevant information from the observed state $\mathbf{s}_t$.

>>>>

Consider a \gls{va} contract whose delta hedge portfolio at any time~$t$, $t=0,1,\ldots,T-1$, consists of $\Delta_t$ units in the underlying stock and $B_t$ amount of a risk-free zero-coupon bond maturing at time $T$.
The value of the hedge portfolio at time~$(t-1)$ is:
\begin{equation*}
    H_{t-1} = \Delta_{t-1} S_{t-1} + B_{t-1},
\end{equation*}
where $S_t$ is the underlying stock price and any time $t>0$.
This hedge portfolio is brought forward to the next rebalancing time~$t$, when its value becomes:
\begin{equation*}
    H_{t}^{bf} = \Delta_{t-1} S_{t} + B_{t-1}e^{-rt}.
\end{equation*}
Therefore, the time~$t$ hedging error, i.e., the cash flow incurred by the insurer due to rebalancing at time~$t$, is
\begin{equation}
    HE_t = H_t - H^{bf}_t, \quad t=1,\ldots, T-1.
\end{equation}
The P\&L of the \gls{va} contract includes the cost of the initial hedge ($H_0$), the hedging errors~\eqref{eq2:hedgingerror}, the unwinding of the hedge at maturity ($H^{bf}_T$), and the contract payout at time~$t\in \{0,\ldots,T\}$.
Mathematically, the present value of the liability for a \gls{gmmb} contract is 
\begin{align} \label{eq3:lossGMMB}
L   & = H_0 - e^{-rT} H^{bf}_T + \sum_{t=1}^{T-1} e^{-rt} HE_t + \sum_{t=1}^T e^{-rt} C_t - \sum_{t=1}^T e^{-rt} F_t\eta_n + e^{-rT} (G_t - F_t)^+  \nonumber \\ 
    & = e^{-rT} (G_T - F_{T^+})^+ + \sum_{t=1}^T e^{-rt}  \left( \Delta_{t-1} (S_{t-1} - e^{-r} S_t) + C_t - F_t\eta_n \right) 
\end{align}
where the equality holds by a rearrangement of terms and a telescopic sum simplification of $e^{-rt}B_t$, $t=0,\ldots,T-1$, and $C_t := C \cdot S_{t-1} \cdot |\Delta_t - \Delta_{t-1}|$ is the tranaction cost at time $t$~\citep{garleanu2013dynamic}.
Hence, the present liability consist of the hedging errors, the transaction costs, the net management fees, and the contract payouts.
Similarly, the present value of the liability for a \gls{gmwb} contract is
\begin{equation} \label{eq3:lossGMWB}
L = \sum_{t=1}^T e^{-rt}  \left( \Delta_{t-1} (S_{t-1} - e^{-r} S_t) + C_t - F_t\eta_n \right)
\end{equation}
The \gls{gmwb} payout is implicitly included in $F_t\eta_n$.
Both Equation~\eqref{eq3:lossGMMB} and Equation~\eqref{eq3:lossGMWB} neglect the transaction cost to liquidate the hedge portfolio at maturity.
The discrete-time hedging problem of VAs can be conveniently formulated as an \gls{mdp}, where the states, actions, transition probabilities, policies, and rewards are defined as follows.
\textcolor{red}{Different from the formulation in Chapter~\ref{chap:project2}, the hedging weight $\Delta_0, \ldots, \Delta_{T-1}$ are not estimated from inner simulation steps but are directly controlled by a \gls{drl} agent.
Thus, the hedging weight $\Delta_t$ at time $t$ is estimated using a neural network whose input is the state $\mathbf{s}_t$ and output is $\Delta_t$.}

\subsection{State Space}
The state space $\mathcal{S}$ represents all the information needed to characterize the hedging environment.
In a \gls{va} hedging problem, $\mathbf{s}_t$, the information available to a hedging agent at each time $t$ is 
$$\mathbf{s}_t := (S_t, F_t, G_t, \tau, \Delta_{t-1}) \in \mathcal{S}.$$
where $\tau$ is the remaining time to maturity and $\Delta_{t-1}$ is the previous hedging weight.
The hedging environment is partially observed, e.g., the agent does not have access to the contract specifications.
It has to learn a representation of the relevant information from the observed state $\mathbf{s}_t$.

### 2025-04-19 project1/nsSurvey.tex
asd

In Equation~\eqref{eq1:mse-sns}, the last equality follows from Assumption~\ref{as1:sns}.
The analysis of the first term is different for smooth and Lipschitz continuous $h$. 
We will analyze them separately below.

@@

The left part of Figure \ref{fig1:reg_lb} contains the \gls{mse}s of the regression procedure for budget sizes that are smaller than $10^3$. 
Slopes of the fitted lines on the left correspond to the empirical rate of convergence of the regression procedure for budget levels between $10^3$ and $10^4$.
To investigate the convergence behavior for higher budget levels, we conduct additional experiments for the European call option with a dimension of $20$. 
The additional experiments are summarized on the right side of Figure \ref{fig1:reg_lb}.
After reaching a certain budget level, i.e., $\Gamma = 10^6$ in our case, the empirical rate of convergence for the regression-based nested simulation procedure approaches its asymptotic rate. 
For nested simulation procedures with a biased metamodel, the metamodel estimates of the true inner simulation are poor, especially for smaller budget sizes. 
We are able to clearly observe this phenomenon for the regression metamodel, and it can be explained by dividing the \gls{mse} into metamodeling bias and simulation variance.
\begin{itemize}
    \item For small budget sizes, the improvement in the bias of the regression metamodel dominates the improvement in the simulation variance. 
    Performing poorly for extremely low simulation budgets, the regression metamodel improves dramatically as the simulation budget increases.
    \item As the simulation budget gets higher, the improvement of the regression bias becomes negligible compared with that of the simulation variance. 
    The regression metamodel ceases to improve after reaching a certain level ($\Gamma = 10^6$ in our case), and the improvement of simulation variance dominates.
\end{itemize}
Due to high computational costs, we are not able to conduct experiments for higher budget levels, but we expect the \gls{mse} of the regression-based nested simulation procedure to stabilize after $\Gamma = 10^6$, and the empirical rate of convergence to approach its asymptotic rate.
In the context of nested simulation procedures, a parametric regression metamodel has several advantages over a non-parametric regression metamodel.
\begin{itemize}
    \item Parametric regression achieves a good empirical convergence behavior for a moderate simulation budget.
    \item Parametric regression is insensitive to changes in the asset dimension.
    \item Parametric regression is easier to implement.
    It does not require cross-validation to select the hyperparameters of the metamodel.
\end{itemize}
However, parametric regression suffers from the model misspecification risk.
More specifically, selecting a wrong regression basis can lead to a poor metamodel estimate, where the \gls{mse} of the nested simulation procedure is dominated by the model error of the metamodel~\citep{broadie2015risk}.

>>>>

\textcolor{red}{In Equation~\eqref{eq1:mse-sns}, the first inequality follows from Cauchy-Schwarz inequality.
One way to express the Cauchy-Schwarz inequality is 
$(x_1y_1 + x_2y_2)^2 \leq (x_1^2 + x_2^2)(y_1^2 + y_2^2)$.
Let $\mathbf{x} = (x_1, x_2)$ and $\mathbf{y} = (y_1, y_2)$.
The Cauchy-Schwarz inequality can be written as}
\begin{equation*}
    \langle \mathbf{x}, \mathbf{y} \rangle^2  = \left( \Vert \mathbf{x} \Vert \cdot \Vert \mathbf{y} \Vert \cdot \cos a \right)^2 \leq \Vert \mathbf{x} \Vert^2 \cdot \Vert \mathbf{y} \Vert^2.
\end{equation*}
\textcolor{red}{By setting $x_1 = \rho_{M,N}- \rho_M$, $x_2 = \rho_M - \rho$, $y_1 = y_2 = 1$, we have }
\begin{align*}
    \left( \rho_{M,N} - \rho_M + \rho_M - \rho \right)^2 
    & \leq \left( (\rho_{M,N} - \rho_M)^2 + (\rho_M - \rho)^2 \right) \left( 1^2 + 1^2 \right) \\
    & = 2 \left( (\rho_{M,N} - \rho_M)^2 + (\rho_M - \rho)^2 \right) \\
    & = 2  (\rho_{M,N} - \rho_M)^2 + 2 (\rho_M - \rho)^2.
\end{align*}
The last equality follows from Assumption~\ref{as1:sns}.
The analysis of the first term is different for smooth and Lipschitz continuous $h$. 
We will analyze them separately below.

@@

The left part of Figure \ref{fig1:reg_lb} contains the \gls{mse}s of the regression procedure for budget sizes that are smaller than $10^3$. 
Slopes of the fitted lines on the left correspond to the empirical rate of convergence of the regression procedure for budget levels between $10^3$ and $10^4$.
To investigate the convergence behavior for higher budget levels, we conduct additional experiments for the European call option with a dimension of $20$. 
The additional experiments are summarized on the right side of Figure \ref{fig1:reg_lb}.
After reaching a certain budget level, i.e., $\Gamma = 10^6$ in our case, the empirical rate of convergence for the regression-based nested simulation procedure approaches its asymptotic rate. 
For nested simulation procedures with a biased metamodel, the metamodel estimates of the true inner simulation are poor, especially for smaller budget sizes. 
We are able to clearly observe this phenomenon for the regression metamodel, and it can be explained by dividing the \gls{mse} into metamodeling bias and simulation variance.
\begin{itemize}
    \item For small budget sizes, the improvement in the bias of the regression metamodel dominates the improvement in the simulation variance. 
    Performing poorly for extremely low simulation budgets, the regression metamodel improves dramatically as the simulation budget increases.
    \item As the simulation budget gets higher, the improvement of the regression bias becomes negligible compared with that of the simulation variance. 
    The regression metamodel ceases to improve after reaching a certain level ($\Gamma = 10^6$ in our case), and the improvement of simulation variance dominates.
\end{itemize}
Due to high computational costs, we are not able to conduct experiments for higher budget levels, but we expect the \gls{mse} of the regression-based nested simulation procedure to stabilize after $\Gamma = 10^6$, and the empirical rate of convergence to approach its asymptotic rate.
\textcolor{red}{The empirical convergence rates reported in the graph legends are higher than the actual rates after regression-based nested simulation procedure reaches the asymptotic convergence regime.}
In the context of nested simulation procedures, a parametric regression metamodel has several advantages over a non-parametric regression metamodel.
\begin{itemize}
    \item Parametric regression achieves a good empirical convergence behavior for a moderate simulation budget.
    \item Parametric regression is insensitive to changes in the asset dimension.
    \item Parametric regression is easier to implement.
    It does not require cross-validation to select the hyperparameters of the metamodel.
\end{itemize}
However, parametric regression suffers from the model misspecification risk.
More specifically, selecting a wrong regression basis can lead to a poor metamodel estimate, where the \gls{mse} of the nested simulation procedure is dominated by the model error of the metamodel~\citep{broadie2015risk}.

### 2025-04-19 project2/nnMetamodels.tex
asd

Estimating tail risk measures of portfolios of complex \gls{va}s usually requires nested simulation.
In the nested simulation, the outer simulation involves projecting scenarios of key risk factors under a $\mathbb{P}$ measure, while the inner simulations are used to value payoffs uder guarantees of varying complexity, under a $\mathbb{Q}$ measure.

For insurers, large-scale nested simulations for assessing \gls{va} losses are generally computationally intensive; i.e., a large number of outer level simulations are needed to estimate extreme tails for calculations of tail risk measures, and a large number of inner simulations are also needed at each time step, because the embedded options are out of money. 
In addition, the required calculations need to be repeated for each \gls{va} contract, or cluster of \gls{va} contracts.
Consequently, insurers are interested in techniques for nested simulation models that produce accurate results within the confines of a finite computational budget.

There are two main approaches that can be used to improve the efficiency of inner simulations.
The first one uses a dynamic, non-uniform allocation of the inner simulation budget, and the second uses a proxy model to replace the inner simulation step.
Some work uses a combination of both approaches.

In Chapter~\ref{chap:project1}, the likelihood ratio approach is used to allocate the inner simulation budget using likelihood ratio weights, i.e., importance sampling.
Proxy models are tractable analytic functions or flexible empirical functions that are used to replace the inner simulation stage of a nested simulation.
Empirical proxies may be intrinsic or extrinsic to the simulation process. Extrinsic proxy functions are selected to be close to the inner simulation values and therefore require detailed information about the payoffs that are evaluated in the inner simulation step. 
Empirical proxies are constructed by using an initial pilot simulation to develop factors or functionals that can subsequently be used in place of the inner simulation. 
A prominent expirical proxy method discussed in the literature is the least squares Monte Carlo method~\citep{longstaff2001valuing}.
In Chapter~\ref{chap:project1}, supervised learning models, including linear regression, \gls{knn}, and \gls{krr}, are used as proxy models for inner simulations.
This chapter introduces a proxy model to reduce the computational requirements of inner simulations of \gls{va}s by replacing the inner simulation step of a nested simulation procedure. 
This proxy model is chosen to be a flexible empirical function, i.e., a \gls{dnn} metamodel.

@@

For an inner simulation path $\Stilde_{t+1},\ldots,\Stilde_{T}$ of the \gls{gmwb} contract, the sensitivity of $V_t$ can be calculated by the following recursion:
\begin{equation}
    \sum_{s=t+1}^{T} e^{-r(T-s)} \left[\bm{1}\{\Itilde_{t,s} > \Ftilde_{t,s}\} \cdot \left( \frac{\partial \Itilde_{t,s}}{ \partial S_t} - \frac{\partial \Ftilde_{t,s}}{ \partial S_t}\right)- \eta_n \frac{\partial \Ftilde_{t,s}}{ \partial S_t}\right], \nonumber \\
    t=0,\ldots,T-1, 
\end{equation}
where $\bm{1}\{\cdot\}$ is an indicator function, $\Stilde_t = (S_{t, t+1},\ldots,S_{t, T})$, $\Ftilde_t = (F_{t, t+1},\ldots,F_{t, T})$, $\Gtilde_t = (G_{t, t+1},\ldots,G_{t, T})$, $\Itilde_t = (I_{t, t+1},\ldots,I_{t, T})$, and
\begin{align} \label{eq2:partial-derivatives}
    \frac{\partial \Ftilde_{t, s}}{ \partial S_t} &= \bm{1}\{\Itilde_{t, s-1} < \Ftilde_{t, s-1}\}\cdot\left( \frac{\partial \Ftilde_{t, s-1}}{ \partial S_t} - \frac{\partial \Itilde_{t, s-1}}{ \partial S_t}\right) \cdot \frac{\Stilde_{t, s}}{\Stilde_{t, s-1}}\cdot (1-\eta_g),\nonumber \\
    \frac{\partial \Gtilde_{t, s}}{ \partial S_t} &= \bm{1}\{\Gtilde_{t, s-1} < \Ftilde_{t, s}\}\cdot\frac{\partial \Ftilde_{t, s}}{ \partial S_t} + \bm{1}\{\Gtilde_{t, s-1} \geq \Ftilde_{t, s}\}\cdot\frac{\partial \Gtilde_{t, s-1}}{ \partial S_t},\nonumber \\
    \frac{\partial \Itilde_{t, s}}{ \partial S_t} &= \gamma \frac{\partial \Gtilde_{t, s}}{ \partial S_t}.
\end{align}
At each inner simulation, the sample path at $t$ is initialized as:
\begin{equation}
    (\tilde{X}_{t, t}) = (\tilde{S}_{t, t}, \tilde{F}_{t, t}, \tilde{G}_{t, t}) = (S_t, F_t, G_t) = (X_t)
\end{equation}
Before withdrawal at $t$, the partial derivatives are initialized. $\tilde{F}_{t, t}$ is set to be proportional to $\tilde{S}_{t}$, such that:
\begin{equation}
    \frac{\partial \Ftilde_{t, t}}{ \partial S_t} = \frac{\partial F_t}{ \partial S_t} = \frac{F_t}{S_t},
\end{equation}
and $\tilde{G}_{t, t}$ and $\tilde{I}_{t, t}$ are fixed as constants, such that:
\begin{equation}
    \frac{\partial \Gtilde_{t, t}}{ \partial S_t} = \frac{\partial G_{t}}{ \partial S_t} = 0, \quad \frac{\partial \Itilde_{t, t}}{ \partial S_t} = \gamma \frac{\partial I_{t}}{ \partial S_t} = 0.
\end{equation}
Note that in Equation~\ref{eq2:partial-derivatives}, no calculation is needed for $F_t \leq I_t$. 
In this case, the sub-account is already depleted at time $t$ and withdrawals are not allowed.
Therefore, \gls{gmwb}'s future liabilities beyond time $t$ are no longer affected by the stock price $S_t$, so no hedging is necessary.
In other words, when $F_t < I_t$, the inner simulation can be skipped and set $\Delta_t = 0$.

@@

  & = B_0 + S_0 V_0 + \sum_{t=1}^{T-1} e^{-rt} \left( B_t + S_t \Delta_t - B_{t-1} \frac{e^{-r(t-1)}}{e^{-rt}} - S_{t-1} \Delta_{t-1}  \right) - e^{-rT} S_T \Delta_{T-1} + V_0,  \nonumber 

@@

>>>>

\textcolor{red}{Estimating tail risk measures of portfolios of complex \gls{va}s usually requires nested simulation.
In the nested simulation, the outer simulation involves projecting scenarios of key risk factors under a $\mathbb{P}$ measure, while the inner simulations are used to value payoffs uder guarantees of varying complexity, under a $\mathbb{Q}$ measure.}

\textcolor{red}{For insurers, large-scale nested simulations for assessing \gls{va} losses are generally computationally intensive; i.e., a large number of outer level simulations are needed to estimate extreme tails for calculations of tail risk measures, and a large number of inner simulations are also needed at each time step, because the embedded options are out of money. 
In addition, the required calculations need to be repeated for each \gls{va} contract, or cluster of \gls{va} contracts.
Consequently, insurers are interested in techniques for nested simulation models that produce accurate results within the confines of a finite computational budget.}

\textcolor{red}{There are two main approaches that can be used to improve the efficiency of inner simulations.
The first one uses a dynamic, non-uniform allocation of the inner simulation budget, and the second uses a proxy model to replace the inner simulation step.
Some work uses a combination of both approaches.}

\textcolor{red}{In Chapter~\ref{chap:project1}, the likelihood ratio approach is used to allocate the inner simulation budget using likelihood ratio weights, i.e., importance sampling.
Proxy models are tractable analytic functions or flexible empirical functions that are used to replace the inner simulation stage of a nested simulation.
Empirical proxies may be intrinsic or extrinsic to the simulation process. Extrinsic proxy functions are selected to be close to the inner simulation values and therefore require detailed information about the payoffs that are evaluated in the inner simulation step. 
Empirical proxies are constructed by using an initial pilot simulation to develop factors or functionals that can subsequently be used in place of the inner simulation. 
A prominent expirical proxy method discussed in the literature is the least squares Monte Carlo method~\citep{longstaff2001valuing}.
In Chapter~\ref{chap:project1}, supervised learning models, including linear regression, \gls{knn}, and \gls{krr}, are used as proxy models for inner simulations.
This chapter introduces a proxy model to reduce the computational requirements of inner simulations of \gls{va}s by replacing the inner simulation step of a nested simulation procedure. 
This proxy model is chosen to be a flexible empirical function, i.e., a \gls{dnn} metamodel.}

@@

For an inner simulation path $\Stilde_{t+1},\ldots,\Stilde_{T}$ of the \gls{gmwb} contract, the sensitivity of $V_t$ can be calculated by the following recursion:
\begin{equation}
    \sum_{s=t+1}^{T} e^{-r(T-s)} \left[\bm{1}\{\Itilde_{t,s} > \Ftilde_{t,s}\} \cdot \left( \frac{\partial \Itilde_{t,s}}{ \partial S_t} - \frac{\partial \Ftilde_{t,s}}{ \partial S_t}\right)- \eta_n \frac{\partial \Ftilde_{t,s}}{ \partial S_t}\right], \nonumber \\
    t=0,\ldots,T-1, 
\end{equation}
where $\bm{1}\{\cdot\}$ is an indicator function, $\Stilde_t = (S_{t, t+1},\ldots,S_{t, T})$, $\Ftilde_t = (F_{t, t+1},\ldots,F_{t, T})$, $\Gtilde_t = (G_{t, t+1},\ldots,G_{t, T})$, $\Itilde_t = (I_{t, t+1},\ldots,I_{t, T})$, and
\begin{align} \label{eq2:partial-derivatives}
    \frac{\partial \Ftilde_{t, s}}{ \partial S_t} &= \bm{1}\{\Itilde_{t, s-1} < \Ftilde_{t, s-1}\}\cdot\left( \frac{\partial \Ftilde_{t, s-1}}{ \partial S_t} - \frac{\partial \Itilde_{t, s-1}}{ \partial S_t}\right) \cdot \frac{\Stilde_{t, s}}{\Stilde_{t, s-1}}\cdot (1-\eta_g),\nonumber \\
    \frac{\partial \Gtilde_{t, s}}{ \partial S_t} &= \bm{1}\{\Gtilde_{t, s-1} < \Ftilde_{t, s}\}\cdot\frac{\partial \Ftilde_{t, s}}{ \partial S_t} + \bm{1}\{\Gtilde_{t, s-1} \geq \Ftilde_{t, s}\}\cdot\frac{\partial \Gtilde_{t, s-1}}{ \partial S_t},\nonumber \\
    \frac{\partial \Itilde_{t, s}}{ \partial S_t} &= \gamma \frac{\partial \Gtilde_{t, s}}{ \partial S_t}.
\end{align}
At each inner simulation, the sample path at $t$ is initialized as:
\begin{equation}
    (\tilde{S}_{t, t}, \tilde{F}_{t, t}, \tilde{G}_{t, t}) = (S_t, F_t, G_t) 
\end{equation}
Before withdrawal at $t$, the partial derivatives are initialized. $\tilde{F}_{t, t}$ is set to be proportional to $\tilde{S}_{t}$, such that:
\begin{equation}
    \frac{\partial \Ftilde_{t, t}}{ \partial S_t} = \frac{\partial F_t}{ \partial S_t} = \frac{F_t}{S_t},
\end{equation}
and $\tilde{G}_{t, t}$ and $\tilde{I}_{t, t}$ are fixed as constants, such that:
\begin{equation}
    \frac{\partial \Gtilde_{t, t}}{ \partial S_t} = \frac{\partial G_{t}}{ \partial S_t} = 0, \quad \frac{\partial \Itilde_{t, t}}{ \partial S_t} = \gamma \frac{\partial I_{t}}{ \partial S_t} = 0.
\end{equation}
Note that in Equation~\ref{eq2:partial-derivatives}, no calculation is needed for $F_t \leq I_t$. 
In this case, the sub-account is already depleted at time $t$ and withdrawals are not allowed.
Therefore, \gls{gmwb}'s future liabilities beyond time $t$ are no longer affected by the stock price $S_t$, so no hedging is necessary.
In other words, when $F_t < I_t$, the inner simulation can be skipped and set $\Delta_t = 0$.

@@

  & = B_0 + S_0 V_0 + \sum_{t=1}^{T-1} e^{-rt} \left( B_t + S_t \Delta_t - B_{t-1} \frac{e^{-r(t-1)}}{e^{-rt}} - S_{t-1} \Delta_{t-1}  \right) - e^{-rT} S_T \Delta_{T-1} + V_0,  

@@

\textcolor{red}{In the two-stage procedure, the neural network metamodel approximates $L$ in Equation~\ref{eq2:lossrv}, where }
\begin{equation}
    L = L(\mathbf{S}_T) = L(\Delta_0, \ldots, \Delta_{T-1}, S_0, \ldots, S_T)
\end{equation}
\textcolor{red}{The loss $L$ depends on all the hedging weights $\Delta_0, \ldots, \Delta_{T-1}$, which are determined by the stock prices $S_t$, $t=0,\ldots,T-1$.}
\textcolor{red}{In addition, $L$ also depends on all the stock prices $S_0, \ldots, S_T$ directly.}
\textcolor{red}{Therefore, the loss $L(\mathbf{S}_T)$ is a complex function of the entire stock price path $\mathbf{S}_T$, and the neural network metamodel $\Lhat^{PD}(\mathbf{X})$ approximates $L(\mathbf{S}_T)$ by mapping the stock returns $\mathbf{X}_T$ to the loss $L(\mathbf{S}_T)$.}
\textcolor{red}{Statistically speaking, $L(\mathbf{S}_T)$ is a random variable whose stochasticity solely depends on the stock price path $\mathbf{S}_T$. }
\textcolor{red}{Nevertheless, $L(\mathbf{S}_T)$ can be viewed as a function of the underlying stock returns $\mathbf{X}_T$ and can be approximated by a neural network metamodel.}
